Grove: A Convergent Collaborative Structure-Editor Calculus

### 2022-08-10 introduction.tex
add some intro notes w/ cyrus

>>>>

start with something that everyone can accept: ``programming is collaborative.''

briefly introduce 3 types: diff, OT, CRDT

tease out some common problems (tree-native, collaborative)

propose a solution

general motivation: programming is a collaborative activity

today usually takes the form of coarse-grained solutions, e.g, git

if you try to use eg google docs for this, there are several problems
(gap problem, diffs don't handle repositioning well)

diff is not really an ideal way of communicating change: e.g., how repositioning gets mishandled

CRDT: tree-native vs text. think about obvious limitation of existing tools

algorithms for collaborative text editing are well developed
natural fit for text
not a natural fit for trees
so if you want to build a grove, a more natural approach is needed

a lot of collaborative editing of other sorts (not necessarily programming) requires a tree model,
but that problem doesn't seem to have been study directly (maybe except JSON CRDT).
